\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-27 Report/project_report.tex
Added swf math to paper

% Custom math defs
\def\Vec#1{\mathbf{#1}}
\newcommand{\bbm}{\begin{bmatrix}}
\newcommand{\ebm}{\end{bmatrix}}

@@

[BATCH MATH GOES HERE?]

>>>>

% Custom math defs
\def\Vec#1{\mathbf{#1}}
\newcommand{\bbm}{\begin{bmatrix}}
\newcommand{\ebm}{\end{bmatrix}}
\DeclareMathAlphabet{\mbf}{OT1}{ptm}{b}{n}
\newcommand{\mbs}[1]{{\boldsymbol{#1}}}
\newcommand{\pd}[2]{\frac{\partial #1}{\partial #2}}

@@

\begin{equation}
(\mbf H^T \mbf T ^{-1} \mbf H ) \delta \mbf{x}^*  = - \mbf{H}^T\mbf{T}^{-1}\mbf{e}(\bar{\mbf{x}})
\end{equation}

\begin{equation}
\delta\mbf{x} := \bbm \delta \mbf x_0 \\ \vdots \\ \delta \mbf x_K \\ \delta \mbf f_1 \\ \vdots \\ \delta \mbf f_N\ebm,
\end{equation}
where $N$ is the number of unique features observed in the window and 
\begin{equation}
\mathbf{H} := \begin{bmatrix}
 -\mbf H_{\mbf x, 1} & \mbf 1 & &  & &   \\ 
 & -\mbf G_{\mbf x, 1} &  &  &  &   -\mbf G_{\mbf f, 1} \\ \hline
 & -\mbf H_{\mbf x, 2} & \mbf 1 & & &    \\ 
 & & -\mbf G_{\mbf x, 2} &  & &  -\mbf G_{\mbf f, 2}   \\ \hline
 &  & \ddots & \ddots & & \vdots  \\  \hline
  & & & -\mbf H_{\mbf x, K} & \mbf 1 & \\ 
 & & & & -\mbf G_{\mbf x, K} &  -\mbf G_{\mbf f, K}   \\  
\end{bmatrix}, 
\end{equation},

\begin{equation}
\mbf G_{\mbf x, k}^j := \pd{\mbf g}{ \mbf p}\Bigr|_{\mbf p = \bar{\mbf p}_{c_k}^{p_j c_k}} \bbm -\mbf C_{cv} \mbf C_{v_k i} & \mbf C_{cv} (\mbf C_{v_k i} (\pmb{\rho}_i^{p_j i} - \mbf r_i^{v_k i} ) )^\times  \ebm\end{equation}

\begin{equation}
\quad \mbf G_{\mbf x, k} := \bbm \mbf G_{\mbf x, k}^1 \\ \vdots \\ \mbf G_{\mbf x, k}^M \ebm
\end{equation}

\begin{equation}
\mbf G_{\mbf f, k}^j := \pd{\mbf g}{ \mbf p}\Bigr|_{\mbf p = \bar{\mbf p}_{c_k}^{p_j c_k}} \bbm \mbf C_{cv} \mbf C_{v_k i}\ebm\end{equation}

\begin{equation}
\quad \mbf G_{\mbf f, k} := \underbrace{\bbm \mbf G_{\mbf f, k}^1 & & \\ & & \mbf G_{\mbf f, k}^2 & \\ & & \vdots &  \\ & & & \mbf G_{\mbf f, k}^M \ebm}_{\text{$j$th block column position given by feature id $n$}} \in \Real^{4M \times 3N}
\end{equation}

and,
\begin{equation}
\bar{\mbf p}_{c_k}^{p_j c_k} := \bbm x \\ y \\ z \ebm = \mbf C_{cv} \left( \mbf C_{v_k i} (\pmb{\rho}_i^{p_j i} - \mbf r_i^{v_k i} )   - \pmb \rho_v^{cv} \right),
\end{equation}

\begin{equation}
\pd{\mbf g}{ \mbf p}\Bigr|_{\mbf p = \bar{\mbf p}_{c_k}^{p_j c_k}} = \bbm \frac{f_u}{z} & 0 & -\frac{1}{z^2} f_u x \\  0 & \frac{f_v}{z} & -\frac{1}{z^2} f_v y  \\ \frac{f_u}{z} & 0 & -\frac{1}{z^2} f_u (x-b) \\  0 & \frac{f_v}{z} & -\frac{1}{z^2} f_v y\ebm.
\end{equation}
or for monocular,
\begin{equation}
\pd{\mbf g}{ \mbf p}\Bigr|_{\mbf p = \bar{\mbf p}_{c_k}^{p_j c_k}} = \bbm \frac{f_u}{z} & 0 & -\frac{1}{z^2} f_u x \\  0 & \frac{f_v}{z} & -\frac{1}{z^2} f_v y \ebm.
\end{equation}
